---
title: "hw2"
author: "Yuchen Zeng"
date: "9/28/2019"
output: html_document
---

# Name: Yuchen Zeng
# Netid: yzeng58

## Summary
First I tried the given simpliest distance function and ignored all the points with parameter and_mask == 0. However, my functions always returned error when it ran to the 97th observation. Then, I realized this is because the and_mask of all the points in the 97th observation is nonzero. So I revised my functions. It did not return error again. Nevertheless, the observations with shortest distance did not seem fit well with our target spectrum. Then I found the cause: the scale. Eventually, I got the final result. Actually, I met many other difficulties before I ran to final result, but they are to trivial to be mentioned. 

Here is my result.

```{r setup, include=FALSE}
detect = read.csv("hw2.csv", header = TRUE)
detect
```

## Date Processing

```{r}
require(ggplot2)
require(astro)
wd = getwd()
template = read.fitstab("cB58_Lyman_break.fit")
target = template[,2]
setwd(paste(getwd(),"/data",sep=""))
spectrum.id = list.files()
spectrum = lapply(spectrum.id,FUN=read.fitstab)
setwd(wd)
```

## Figures Drawing
```{r}
for (i in 1:3){
  spec1 = read.fitstab(paste("data/",as.character(detect$spectrumID[i]),sep=""))
  figure1 = data.frame(x = c(1:dim(spec1)[1], 1:dim(spec1)[1]), 
                     y = c(scale(spec1[,1]),c(rep(0,detect[1,3]-1),scale(target),rep(0,dim(spec1)[1]-length(target)-detect[1,3]+1))),
  spectrum = c(rep(as.character(detect$spectrumID[i]), dim(spec1)[1]), rep("cB58_Lyman_break.fit", dim(spec1)[1])))

  print(ggplot(data=figure1, aes(x = x, y = y, color = spectrum))+geom_line()+
          labs(x="shifted wavelength", y = "rescaled flux"))
}
```


